Notes on the low density parameters in {\tt MAESTRO}

### 2009-02-17 docs/lo_density/lo_density.tex
more updates - this now fully reflects what the code is doing

@@

\item After each call to {\tt correct\_base} in spherical 
  (or call to {\tt average} in plane-parallel.

@@

\item In {\tt probin}, {\tt anelastic\_cutoff} is set to $3\times 10^6$
  by default.

@@

\item In {\tt probin}, {\tt base\_cutoff\_density} is set to $3\times 10^6$
  by default.

\item In {\tt base\_state}, we abort the program if {\tt
  anelastic\_cutoff} $<$ {\tt base\_cutoff\_density}.

\item In {\tt base\_state}, we compute a physical cutoff location,
  {\tt base\_cutoff\_density\_loc}, which is defined as the physical
  location of the first cell-center at the coarsest level for which
  $\rho_0 <$ {\tt base\_cutoff\_density}.

@@

\item In {\tt make\_hgrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt make\_macrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt make\_w0}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt mkscalforce} subroutine {\tt mkrhohforce}, for
  $r\in[{\tt base\_cutoff\_density\_coord},{\tt r\_end\_coord}]$ we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

\item In {\tt makeRhoHfromP}, the base state pressure at edges is
  computed differently based on where we are in relation to the {\tt
    base\_cutoff\_density}.  For $r\in[{\tt r\_start\_coord},{\tt
      base\_cutoff\_density\_coord}-1]$ we integrate $\rho g$ from the
  nearest cell-centered $p_0$ value.  Otherwise, we just use the
  cell-centered value above the edge.

\item In {\tt update\_scal}, if the new $\rho$ is less than {\tt
  base\_cutoff\_density}, we call the EOS to compute $\rho h$.

>>>>

\item In {\tt probin}, {\tt anelastic\_cutoff} and {\tt base\_cutoff\_density} are
  set to $3\times 10^6$ by default.

\item In {\tt probin}, {\tt burning\_cutoff\_density} is set to 
  {\tt base\_cutoff\_density}.  There is no option to set 
  {\tt burning\_cutoff\_density} using the inputs file.

@@

\item After each call to {\tt correct\_base} in spherical 
  (or call to {\tt average} in plane-parallel).

@@

@@

\item In {\tt base\_state}, we compute a physical cutoff location,
  {\tt base\_cutoff\_density\_loc}, which is defined as the physical
  location of the first cell-center at the coarsest level for which
  $\rho_0 <$ {\tt base\_cutoff\_density}.  This is a trick used for making
  the data consistent for multiple level problems.

@@

\item In {\tt make\_hgrhs}, {\tt make\_macrhs}, and {\tt make\_w0}, 
  we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt mkrhohforce} for plane-parallel, for
  $r\in[{\tt base\_cutoff\_density\_coord},{\tt r\_end\_coord}]$ we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

\item In {\tt update\_scal}, if the new $\rho$ is less than 
  {\tt base\_cutoff\_density} and {\tt do\_eos\_h\_above\_cutoff},  
  we call the EOS to compute $h$.
